### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Aims.Rmd
Sues edits

<!-- Add aims text here -->
We have consolidated and refined these and other recommended standards for OSHEMs as part of a framework for developing an open source model of youth mental health. In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed with the framework.

>>>>

<!-- Add aims text here -->
We have consolidated and refined these and other recommended guidelines for OSHEMs as part of a framework for developing an open source model of youth mental health. In this paper, we describe our motivation for developing the framework, the rationale for each included standard, the software toolkits we have developed to help meet each standard and a worked example of a modelling project developed using this framework.

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Intro_Short.Rmd
Sues edits

Better guidance about how to implement OSHEMs is required [@Sampson2019]. Adherence to explicit standards is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal. Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models but notably not on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX]. A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].

```{r echo=F}
# ISPOR T & V: 
# a multiapplication model, transparency, validation,
# For a multiapplication model, transparency, validation,
# and reporting are ongoing processes. The multiapplica-
# tion model is described (transparency)24 and validated,25
# and the descriptions and validations are continuously
# updated as science and the model evolve.26 In addition,
# each instantiation of the model is described, validated,
# and reported as each application is done.27
```

>>>>

Better guidance about how to implement OSHEMs is required [@Sampson2019]. Adherence to explicit guidelines is as essential requirement for modelling in healthcare [@Erdemir2020], but current best practice recommendations for OSHEMs are scarce and piecemeal. Guidelines on health economic model transparency were published ten years ago [@Eddy2012] and made recommendations on documenting models; however, notably missing were recommendations on the sharing of model code and data. More recent and more general modelling guidance [@Erdemir2020] recommends the sharing of code and data through platforms such as GitHub [@github2007] and Zenodo [@Zenodo2013] and the use of version control systems such as Git [@git20XX]. A coding framework for OSHEMs developed in the language R includes standardised approaches to directory structure and naming conventions [@Alarid2019].

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Results.Rmd
Sues edits

Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23]. The large and widespread additional mental health burdens recently observed during the COVID pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].

<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.  -->
Open source frameworks have been previously recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare. Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is also being developed as part of the Open Value Initiative [@Jansen2019]. Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.

Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives. Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020]. Currently, mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex systems [@RN73]. Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might also be the basis for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams. However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].

To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021]. There are significant deficits in our understanding of the systems in which mental disorder emerges and is treated [@Fried2020] and longer term project horizons could allow mental health economic models to progressively improve validity as these gaps are addressed. Currently, the theoretical basis for understanding complex mental health systems is weak [@RN2111]. Strikingly, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context is underdeveloped [@RN42]. There is insufficient evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

@@

## readyforwhatsnext
We are currently developing readyforwhatsnext, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.

Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people. Our in development model of places [@DVN/V3OKZV_2022] aims to synthesise geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with the model.

Our initial work on readyforwhatsnext is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts. Progress is reported on a project website [@rfwn2022].

# Framework
The framework we have developed to implement readyforwhatsnext specifies standards for OSHEMs and provides tools for meeting those standards.

## Framework standards
We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models TIMELY:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomized**: a model and its components can be used in multiple decision contexts;
 - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.

@@

Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update. For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development. Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention. 
Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?, can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

@@

### Epitomised Models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for. A special type of function called a method can only be applied to a pre-defined class of data structure. Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022]. For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.

@@

The six R packages, their primary focus, the TIMELY standards they support and the third party packages they depend on are summarised in Table \@ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards. However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4). Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third party tools with our own in future releases of our software. Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].

@@

# Application
We used framework toolkits to develop model code and datasets for implementing a utility mapping study [@Hamilton2021.07.07.21260129]. Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet. The two current standards where the study falls short are in reporting code coverage and including a user-interface. Both these items are current development priorities for our team.

>>>>

Mental disorders impose high health, social and economic burdens worldwide [@RN8;@GBD2019]. Much of this burden is potentially avertable [@RN25], but poorly financed and organised mental health systems are ill-equipped for this challenge[@RN22;@RN23]. The large and widespread additional mental health burdens recently observed during the COVID-19 pandemic[@20211700] and predicted as a potential future consequence of global heating [@page_howard_2010], highlight the need to improve the resilience and adaptability of these systems. To help stem growing demand for mental health services, policymakers have also been encouraged to place greater emphasis on tackling the social determinants of mental disorder[@RN11].

<!-- Computational modelling could play an important role in developing policies to improve population mental health but this may require significant changes in the way mental health modelling projects are funded, conceptualised and implemented.  -->
Open source frameworks have been recommended for the development of mental health modelling field [@RN73] but, as with health economics more generally, OSHEMs remain rare. Currently there is only one mental health related model (in Alcohol Use Disorder [@Basu2018]) that is indexed in the Open Source Models Clearinghouse [@OSMC_20xx;@Emerson2019]. A Major Depressive Disorder reference model for the United States [@IVIMDD2022] is being developed as part of the Open Value Initiative [@Jansen2019]. Greater use of open source approaches could help improve the scope, validity and usefulness of mental health economic models.

Major mental health reform programs, such as those currently being implemented in Victoria, Australia [@VicRC2021], can involve the identification, prioritisation, sequencing, targeting and monitoring of multiple interdependent initiatives. Single purpose models that assume static systems may be inadequate for the decision support needs of policymakers and service planners [@PC2020]. Mental health economic models predominantly address issues relating to the affordability and value for money of individual programs [@RN34] with mental health simulation studies rarely modelling complex dynamic systems [@RN73]. Systems modelling approaches, that have been recommended for public health economics more generally [@SQUIRES2016588] and for mental health specifically [@Occhipinti2021], could provide greater insight about inter-dependencies between candidate policies and the dynamic nature of the mental health systems planning context. Dynamic systems methods might provide the foundations for developing reference models [@Afzali2013] of mental health systems that are intended for multiple-applications and re-use by different modelling teams. However, more complex models may be more prone to error [@Saltelli2019] and models designed for multiple purposes require greater investments in model transparency and validation [@Eddy2012; @Feenstra2022].

To retain and improve their utility as decision aids, health economic models require updating and refinement as new evidence emerges and decision contexts change [@Jenkins2021]. The significant deficits in our understanding of the systems in which mental disorders emerge and are treated [@Fried2020] suggest that there is ample scope for mental health systems models to progressively improve the validity over time. Prospective work could address the weak theoretical underpinnings for understanding complex mental health systems [@RN2111]. For example, it remains unclear why increased investments in mental health care have yet to discernibly reduce the prevalence and burden of mental disorders[@RN26].  The literature about how the requirements, characteristics and performance of mental health services are shaped by spatiotemporal context needs to be further developed [@RN42]. There is also a need for better evidence to identify the social determinants of mental disorders most amenable to preventative interventions, and for which population sub-groups such interventions would be most effective [@RN43].

@@

## readyforwhatsnext
We are currently developing **readyforwhatsnext**, a reference OSHEM that aims to examine multiple potential population level strategies for promoting mental wellbeing and preventing and treating mental disorders in young people.

Our approach to model development is to undertake a number of discrete modelling projects of the people, places, platforms and programs that shape the mental health and wellbeing of young people and to progressively link them together by means of a common framework. To model people we are developing synthetic representations of populations of interest [@DVN/HJXYKQ_2021] that describe relevant individual characteristics and their relationships, algorithms that map psychological measures to health utility [@Hamilton2021.07.07.21260129] and choice models for predicting the helpseeking behaviour of young people [@hamilton_matthew_2022_6627995]. Our in-development model of places [@DVN/V3OKZV_2022] has the aim of synthesising geometry and spatial attribute data to characterise the geographic distribution of relevant demographic, environmental, epidemiological and service infrastructure features. We are in the early stages of a multi-annual project to develop a service platform model that will represent the processes and operations of a complex primary youth mental health service. We also plan to extend and update our prior work reviewing economic evidence relating to youth mental health programs [@RN33] so that it can be integrated with this model.

Our initial work on **readyforwhatsnext** is focused on Victoria, Australia but the framework we are using to develop it is designed to facilitate extension by ourselves and others to different decision contexts. Progress is reported on a project website [@rfwn2022].

# Framework
The framework we have developed to implement **readyforwhatsnext** specifies standards for OSHEMs and provides tools for meeting those standards.

## Framework standards
We have identified 20 standards that we believe are important for quality implementations of OSHEMs, each described under one of following six principles for making models **TIMELY**:

 - **Transparent**: people can easily see how a model has been implemented and tested;
 - **Iterative**: a model is routinely updated to maintain and improve validity;
 - **Modular**: models and their components can be combined to extend their scope;
 - **Epitomising**: a model and its components can be used in multiple decision contexts;
 - **Licensed**: a model, its components and derivatives are persistently re-usable by other modellers; and
 - **Yielding**: a model can be simply, flexibly and reliably used to inform decision-making.

@@

Adopting semantic versioning [@semver20xx] conventions can be an efficient way to provide users of model code and data with information about the potential importance of an update. For R code, the usethis [@usethis2021] package can be used to partially automate version number increments using the convention Major.Minor.Patch.Development. Datasets stored on the Harvard Dataverse use the simpler Major.Minor convention. 
Continuous integration [@CI2017] tools can help verify that each code update passes multiple quality tests. OSHEMs developed in R can take advantage of templates provided by devtools [@devtools2021] and pkgdown [@pkgdown2022] to run continuous integration checks on GitHub. These tests can include those of units (do individual functions produce expected output?), documentation (does documentation render correctly?; can all example workflows be executed?) and installation (can the software be successfully deployed on multiple types of operating system?).

@@

### Epitomising Models
A key challenge to generalising health economic models is that they are typically developed to inform a decision problem with a highly specific jurisdictional context. However, a number of choices about how these models are implemented can significantly increase the re-usability of model code in other contexts.

Writing code as collections of functions (short, self-contained and reusable algorithms that each perform a discrete task) is recommended as good practice for scientific computing [@Wilson_2017]. When distributed as libraries (for example, as R packages), functions have the potential to be widely re-used, often in contexts very different than those they were originally developed for. A special type of function, called a method, can only be applied to a pre-defined class of data structure. Due to the coding concept of inheritance [@8717448], the more restricted nature of methods can be used to enhance the re-usability of model code in different decision contexts [@ready4oop2022]. For example, when generalising a model developed for the Australian context to a UK context, one could create a class that initially inherits all of the methods defined for the Australian model and then write new or replacement methods as needed for the UK model.

@@

The six R packages, their primary focus, the TIMELY standards they support and the third-party packages they depend on are summarised in Table \@ref(tab:cpkgs). When used in conjunction with framework repositories, the six packages extending existing R packages to provide strong support for implementing 16 of the TIMELY standards. However, the software only weakly supports implementing the standards relating to disseminating statistical models (Y1) and user-interface development (Y2) and does not yet provide any workflow tools to help implement the standards for code coverage (T5) and deprecation conventions (I4). Standards not supported or weakly supported by our software can be met with existing developer tools in R and we plan to progressively integrate these third-party tools with our own in future releases of our software. Another future priority is to submit production versions of each R package for review by and archiving on the Comprehensive R Archive Network (CRAN) [@CRAN2022].

@@

# Application
We used framework toolkits to develop model code and datasets for implementing a utility mapping study that has previously been described [@Hamilton2021.07.07.21260129]. Table \@ref(tab:checktb) assesses that study against each TIMELY standard, 18 of which the study was able to meet. The two current standards where the study falls short are in reporting code coverage and including a user-interface. Both these items are current development priorities for our team.

### 2022-06-10 Markdown/Manuscript/Child_RMDs/MS_Tables_2.Rmd
Sues edits

---
title: "Untitled"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
    #  a <- c("TEST1","TEST2")
    # b <- c("\\cite{ready4show2022}", "hjhjhj")
    # tmp <- data.frame(a,b)   
#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
#  kableExtra::kable_styling(
#    latex_options = c("striped", "hold_position", "repeat_header")
#    ) %>%  
#   kableExtra::column_spec(2, width = "50em") %>%
# kableExtra::landscape()

@@

                                        "Yesg",

@@

                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], <br> 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",

@@

tb2_nms_chr<-colnames(checklist_df)
checklist_df <- data.frame(checklist_df[,1],
                 rep("&nbsp; ",nrow(checklist_df)),
                 checklist_df[,2],
                 rep("&nbsp; &nbsp; &nbsp; &nbsp; ",nrow(checklist_df)),
                 checklist_df[,3],
                 rep("&nbsp; ",nrow(checklist_df)),
                 checklist_df[,4])
colnames(checklist_df) <- c(" "," ","Standard",#
                             "   ","Met?","   ",
                            tb2_nms_chr[4])
if(params$X@outp_formats_chr[1] == "Word") {
  checklist_df %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL)
  }else{
    checklist_df %>%
    kableExtra::kbl(format = "markdown",
                    booktabs = T,
                    caption = knitr::opts_current$get("tab.cap")) 
    }
```

>>>>

---
title: "Untitled"
author: "Author"
date: "`r Sys.Date()`"
output: html_document
---
```{r checktb, tab.cap='TIMELY Checklist applied to utility mapping study', tab.id = 'checktb', echo = F, results = 'asis'}
    #  a <- c("TEST1","TEST2")
    # b <- c("\\cite{ready4show2022}", "hjhjhj")
    # tmp <- data.frame(a,b)   
#     kableExtra::kbl(tmp, booktabs = T, escape = F) %>%
#  kableExtra::kable_styling(
#    latex_options = c("striped", "hold_position", "repeat_header")
#    ) %>%  
#   kableExtra::column_spec(2, width = "50em") %>%
# kableExtra::landscape()

@@

@@

                           Description = c("5 libraries (youthvars, scorz, specific, TTU and youthu) [@hamilton_matthew_2022_6084467; @hamilton_matthew_2022_6084824; @hamilton_matthew_2022_6116701; @gao_caroline_2022_6130155; @matthew_p_hamilton_2021_5646669], 3 programs [@hamilton_matthew_2022_6129906; @hamilton_matthew_2022_6416330; @hamilton_matthew_p_2022_6321821], 2 sub-routines [@hamilton_matthew_2022_6116385; @matthew_p_hamilton_2022_5976988] and 2 datasets [@DVN/DKDIB0_2021; @DVN/HJXYKQ_2021] are permanently archived with unique identifiers.",

@@

tb2_nms_chr<-colnames(checklist_df)
checklist_df <- data.frame(checklist_df[,1],
                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
                               nrow(checklist_df)),
                           checklist_df[,2],
                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; &nbsp; &nbsp; &nbsp; "),
                               nrow(checklist_df)),
                           checklist_df[,3],
                           rep(ifelse(params$X@outp_formats_chr[1] == "Word"," ","&nbsp; "),
                               nrow(checklist_df)),
                 checklist_df[,4])
colnames(checklist_df) <- c(ifelse(params$X@outp_formats_chr[1] == "Word","Code"," "),
                            ifelse(params$X@outp_formats_chr[1] == "Word","YYY"," "),
                            "Standard",#
                             ifelse(params$X@outp_formats_chr[1] == "Word","ZZZ","   "),
                            "Met?",
                            ifelse(params$X@outp_formats_chr[1] == "Word","AAA","   "),
                            tb2_nms_chr[4])
if(params$X@outp_formats_chr[1] == "Word") {
  library("flextable")
  library("ftExtra")
  checklist_df[,
               c(1,3,5,7
                  )] %>%
    ready4show::print_table(output_type_1L_chr = params$X@outp_formats_chr[1],
                            caption_1L_chr = knitr::opts_current$get("tab.cap"),
                            mkdn_tbl_ref_1L_chr = paste0("tab:",knitr::opts_current$get("tab.id")),
                            use_rdocx_1L_lgl = ifelse(params$X@outp_formats_chr[1]=="Word",T,F),
                            add_to_row_ls = NULL,
                            sanitize_fn = NULL) %>%
  ftExtra::colformat_md()
  }else{
    checklist_df %>%
    kableExtra::kbl(format = "markdown",
                    booktabs = T,
                    caption = knitr::opts_current$get("tab.cap")) 
    }
```

### 2022-06-10 Markdown/Manuscript/Parent_PDF/Parent_PDF.Rmd
Sues edits

---
bibliography: ../Data/references.bib
output: 
  bookdown::pdf_book: 
    base_format: rticles::arxiv_article
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
  bookdown::pdf_document2: 
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
    toc: no
## CUSTOM_AUTHORS_PLACEHOLDER ##
params:
  X: NULL
abstract: "There is strong in principle support for open source health economic models, but practical barriers limit their availability. We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomised and Yielding. We then describe a software framework that we have developed for developing TIMELY models in youth mental health and illustrate this framework with an open source utility mapping project."
# abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
graphics: yes
csl: plos.csl
---

>>>>

---
bibliography: ../Data/references.bib
output: 
  bookdown::pdf_book: 
    base_format: rticles::arxiv_article
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
  bookdown::pdf_document2: 
    includes:
      in_header: preamble.tex
    pandoc_args: 
      - "--metadata-file=../Header/header_common.yaml"
      - '--lua-filter=../Filters/scholarly-metadata.lua'
      - '--lua-filter=../Filters/author-info-blocks.lua'
    toc: no
## CUSTOM_AUTHORS_PLACEHOLDER ##
params:
  X: NULL
abstract: "There is strong in principle support for open source health economic models, but practical barriers limit their availability. We propose a set of principles and standards for the implementation of open source health economic models that are TIMELY - Transparent, Iterative, Modular, Epitomising and Yielding. We then describe a software framework that we have developed for developing TIMELY models in youth mental health and illustrate this framework with an open source utility mapping project."
# abstract: "`r paste0(readLines('../Header/abstract.txt'),collapse=' ')`"
graphics: yes
csl: plos.csl
---
